---
title: "Resistance Dashboard"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding=encoding, output_dir = "output") })
---
```{css, echo=FALSE}
#scrollable {
  max-height: 700px; /* Might need changing depending on monitor sizes... */
  overflow-y: scroll; /* Enable vertical scrolling */
}
```

```{r setup packages, include=FALSE}
knitr::opts_chunk$set(
   cache = FALSE,
  fig.height = 5,
  echo = FALSE
)
pacman::p_load(crosstalk, tidyverse, glue, plotly, ggplot2, reshape2)
```

```{r setup load data}
load("output/data/main_table.Rdata")
load("output/data/Dates.Rdata")
load("output/data/isolate_numbers.Rdata")
```

```{js}
const setDefaultValue = function(filterId, defaultValue) {
  window.addEventListener("load", function(event) { 
    document.getElementById(filterId).getElementsByClassName("selectized")[0].selectize.setValue(defaultValue, false);
  });
};
```

```{js}
const removeAllOption = function(filterId) {
  window.addEventListener("load", function(event) {
    var selectizeControl = document.getElementById(filterId).getElementsByClassName("selectized")[0].selectize;
    selectizeControl.removeOption(''); // Remove the "All" option
  });
};
```

# Intro

This is an example of a resistance dashboard.  It is intended as a template for you to use locally and adapt to your needs. 

It is distributed under an MIT license, meaning I can't accept any responsiblity for stuff going wrong as a result of it, but you are completely free to use and adapt it to any end you see fit.

Please note that the data used to make this is fictional and for illustration purposes only.  I have tried to make it roughly true to life but if you spot some odd resistance patterns then that will be why!

Below are some auto-calculations about the pipeline that I think are useful to see:

This pipeline was run on the `r format(Sys.Date(), "%d/%m/%Y")`

It includes isolates from `r format(Start, "%d/%m/%Y")` to the `r format(End, "%d/%m/%Y")`

This dataset includes `r format(isolate_numbers, big.mark = ",")` organisms, from `r format(specimen_numbers, big.mark = ",")` specimens, from `r format(patient_numbers, big.mark = ",")` different patients.

If you would like help localising this or have a problem please open a GitHub issue.  If you want to get in touch or to can't share your question publicaly then email me <a href="mailto:j.goodall8@sheffield.ac.ukc?subject=resistance%20dashboard%20feature%20request"</a>

# All Samples {.tabset}

```{r}
# Create a custom order for the organisms
custom_order_main <- c("Gram Negatives", "Gram Positives", "Enterobacteriaceae", "Anaerobes", "Fungi",  "--------------------", setdiff(sort(unique(main_table$OrgDescrip_new)), c("Gram Negatives", "Gram Positives", "Anaerobes", "Fungi", "Enterobacteriaceae", "--------------------")))

# Re-order the data based on the custom order
main_table <- main_table %>%
  mutate(OrgDescrip_new = factor(OrgDescrip_new, levels = custom_order_main),
         Sensitivity_discrep = factor(Sensitivity_discrep, levels = c("Sensitive", "Increased exposure", "Discrepant phenotype*", "Resistant"))
         ) %>%
         arrange(Antibiotic)

shared_data_main_table <- main_table %>%
  SharedData$new()
```

## Sidebar {.sidebar}

```{r}
# Filter select input with custom order and separator
filter_select("organism_choice", "Choose an organism", shared_data_main_table, ~OrgDescrip_new, multiple = FALSE)
```

```{js}
setDefaultValue("organism_choice", "Gram Negatives");
removeAllOption("organism_choice");
```

*Discrepant phenotype means that the organism is phenotypically sensitive to that antibiotic, but carries a resistance mechanism which would make clinical failure possible.  (e.g an ESBL testing sensitive to co-amoxiclav or a CPE testing sensitive to meropenem.)

## Column

```{r, fig.width=10}
shared_data_main_table %>%
  plot_ly() %>%
  add_bars(
    x = ~percentage, 
    y = ~Antibiotic_new, 
    text = ~paste0("total=", total), 
    textposition = "none",
    cliponaxis = FALSE, 
    outsidetextfont = list(color = "black"),
    color = ~Sensitivity_discrep, 
    colors = c("Resistant" = "darkred", "Sensitive" = "chartreuse3", "Increased exposure" = "orange", "Discrepant phenotype*" = "purple")
  ) %>%
  layout(
    height = 900,  # Set a fixed total height
    xaxis = list(title = "Percentage", range = c(0, 100),
                 categoryorder = "array"),  # Use 'array' to control the ordering
    yaxis = list(
      title = "", 
      categoryorder = "category descending",
      automargin = TRUE,
      tickmode = "linear",
      ticks = "outside", 
      showticklabels = TRUE,
      dtick = 1,
      range = NULL,  # Allows scrolling for more entries than max_visible_entries
      fixedrange = FALSE  # Allow you to scroll through the entries
    ),
    barmode = "stack",
    legend = list(
      title = list(text = "Sensitivity"),
      itemsizing = 'constant',
      orientation = "v",  # vertical orientation
      x = 1.4,  # move the legend to the right
      y = 1,  # move the legend to the top
      xanchor = "right",  # anchor legend to the right
      yanchor = "top",    # anchor legend to the top
      bgcolor = "rgba(255, 255, 255, 0.7)",  # Add a semi-transparent background to avoid overlap
      bordercolor = "black",  # Optional: Add a border for better visibility
      borderwidth = 1  # Optional: Border width
    ),
    margin = list(l = 50, r = 200, b = 50, t = 50, pad = 4)  # Adjust margins to make space for the legend and reduce left blank space
  )
```

# Urines {.tabset}

```{r load urine data}
load("output/data/urine_all_table.Rdata")
load("output/data/urine_IP_table.Rdata")
load("output/data/urine_GP_table.Rdata")
```

```{r}
# Create a custom order for the organisms
custom_order_urine_all <- c("Gram Negatives", "Gram Positives", "Enterobacteriaceae", "Anaerobes", "Fungi",  "--------------------", setdiff(sort(unique(urine_all_table$OrgDescrip_new)), c("Gram Negatives", "Gram Positives", "Anaerobes", "Fungi", "Enterobacteriaceae", "--------------------")))

# Re-order the data based on the custom order
urine_all_table <- urine_all_table %>%
  mutate(OrgDescrip_new = factor(OrgDescrip_new, levels = custom_order_urine_all),
         Sensitivity_discrep = factor(Sensitivity_discrep, levels = c("Sensitive", "Increased exposure", "Discrepant phenotype*", "Resistant"))
         ) %>%
         arrange(Antibiotic)

shared_data_urine_all_table <- urine_all_table %>%
  SharedData$new(~OrgDescrip_new, group = "urine")

urine_IP_table <- urine_IP_table %>%
  mutate(Sensitivity_discrep = factor(Sensitivity_discrep, levels = c("Sensitive", "Increased exposure", "Discrepant phenotype*", "Resistant"))
  ) 


shared_data_urine_IP_table <- urine_IP_table %>%
  SharedData$new(~OrgDescrip_new, group = "urine")

urine_GP_table <- urine_GP_table %>%
  mutate(Sensitivity_discrep = factor(Sensitivity_discrep, levels = c("Sensitive", "Increased exposure", "Discrepant phenotype*", "Resistant"))
  ) 


shared_data_urine_GP_table <- urine_GP_table %>%
  SharedData$new(~OrgDescrip_new, group = "urine")
```

## Sidebar {.sidebar}

```{r}
# Filter select input with custom order and separator
filter_select("organism_choice_urine_all", "Choose an organism", shared_data_urine_all_table, ~OrgDescrip_new, multiple = FALSE)
```

```{js}
setDefaultValue("organism_choice_urine_all", "Gram Negatives");
removeAllOption("organism_choice_urine_all");
```

*Discrepant phenotype means that the organism has tested phenotypically sensitive to that antibiotic, but carries a resistance mechanism which would make clinical failure possible.  (e.g an ESBL testing sensitive to co-amoxiclav or a CPE testing sensitive to meropenem.)

## Column {.tabset}

### All
<div id="scrollable">
```{r, fig.width=10}

  shared_data_urine_all_table %>%
    plot_ly() %>%
    add_bars(
      x = ~percentage, 
      y = ~Antibiotic_new, 
      text = ~paste0("total=", total), 
      textposition = "none",
      cliponaxis = FALSE, 
      outsidetextfont = list(color = "black"),
      color = ~Sensitivity_discrep, 
      colors = c("Resistant" = "darkred", "Sensitive" = "chartreuse3", "Increased exposure" = "orange", "Discrepant phenotype*" = "purple")
    ) %>%
    layout(
      height = 1200,  # Set a fixed total height
      xaxis = list(title = "Percentage", range = c(0, 100),
                   categoryorder = "array"),
      yaxis = list(
        title = "", 
        categoryorder = "category descending",
        automargin = TRUE,
        tickmode = "linear",
        ticks = "outside", 
        showticklabels = TRUE,
        dtick = 1,
        fixedrange = FALSE
      ),
      barmode = "stack",
      legend = list(
        title = list(text = "Sensitivity"),
        itemsizing = 'constant',
        orientation = "v",  
        x = 1.5,  
        y = 1,  
        xanchor = "right",  
        yanchor = "top",    
        bgcolor = "rgba(255, 255, 255, 0.7)",
        bordercolor = "black",
        borderwidth = 1
      ),
      margin = list(l = 50, r = 320, b = 50, t = 50, pad = 4)
    )

```
</div>

### Inpatients Only
<div id="scrollable">
```{r, fig.width=10}
shared_data_urine_IP_table %>%
  plot_ly() %>%
  add_bars(
    x = ~percentage, 
    y = ~Antibiotic_new, 
    text = ~paste0("total=", total), 
    textposition = "none",
    cliponaxis = FALSE, 
    outsidetextfont = list(color = "black"),
    color = ~Sensitivity_discrep, 
    colors = c("Resistant" = "darkred", "Sensitive" = "chartreuse3", "Increased exposure" = "orange", "Discrepant phenotype*" = "purple")
  ) %>%
  layout(
    height = 1200,  # Set a fixed total height
    xaxis = list(title = "Percentage", range = c(0, 100),
                 categoryorder = "array"),  # Use 'array' to control the ordering
    yaxis = list(
      title = "", 
      categoryorder = "category descending",
      automargin = TRUE,
      tickmode = "linear",
      ticks = "outside", 
      showticklabels = TRUE,
      dtick = 1,
      range = NULL,  # Allows scrolling for more entries than max_visible_entries
      fixedrange = FALSE  # Allow you to scroll through the entries
    ),
    barmode = "stack",
    legend = list(
      title = list(text = "Sensitivity"),
      itemsizing = 'constant',
      orientation = "v",  # vertical orientation
      x = 1.5,  # move the legend to the right
      y = 1,  # move the legend to the top
      xanchor = "right",  # anchor legend to the right
      yanchor = "top",    # anchor legend to the top
      bgcolor = "rgba(255, 255, 255, 0.7)",  # Add a semi-transparent background to avoid overlap
      bordercolor = "black",  # Optional: Add a border for better visibility
      borderwidth = 1  # Optional: Border width
    ),
    margin = list(l = 50, r = 320, b = 50, t = 50, pad = 4)  # Adjust margins to make space for the legend and reduce left blank space
  )
```
</div>

### GP Only
<div id="scrollable">
```{r, fig.width=10}
shared_data_urine_GP_table %>%
  plot_ly() %>%
  add_bars(
    x = ~percentage, 
    y = ~Antibiotic_new, 
    text = ~paste0("total=", total), 
    textposition = "none",
    cliponaxis = FALSE, 
    outsidetextfont = list(color = "black"),
    color = ~Sensitivity_discrep, 
    colors = c("Resistant" = "darkred", "Sensitive" = "chartreuse3", "Increased exposure" = "orange", "Discrepant phenotype*" = "purple")
  ) %>%
  layout(
    height = 1200,  # Set a fixed total height
    xaxis = list(title = "Percentage", range = c(0, 100),
                 categoryorder = "array"),  # Use 'array' to control the ordering
    yaxis = list(
      title = "", 
      categoryorder = "category descending",
      automargin = TRUE,
      tickmode = "linear",
      ticks = "outside", 
      showticklabels = TRUE,
      dtick = 1,
      range = NULL,  # Allows scrolling for more entries than max_visible_entries
      fixedrange = FALSE  # Allow you to scroll through the entries
    ),
    barmode = "stack",
    legend = list(
      title = list(text = "Sensitivity"),
      itemsizing = 'constant',
      orientation = "v",  # vertical orientation
      x = 1.5,  # move the legend to the right
      y = 1,  # move the legend to the top
      xanchor = "right",  # anchor legend to the right
      yanchor = "top",    # anchor legend to the top
      bgcolor = "rgba(255, 255, 255, 0.7)",  # Add a semi-transparent background to avoid overlap
      bordercolor = "black",  # Optional: Add a border for better visibility
      borderwidth = 1  # Optional: Border width
    ),
    margin = list(l = 50, r = 320, b = 50, t = 50, pad = 4)  # Adjust margins to make space for the legend and reduce left blank space
  )
```
</div>

